% !TEX root = ../main.tex
% !TEX spellcheck = en-US
\sophia[inline]{How can we use the OT one way, encryption the other way trick from Canetti~\etal~\cite{PKC:CDVW12}?}
In this section, we describe a protocol realizing $\FAKE^{P}$ that uses Yao's garbled circuits~\cite{FOCS:Yao86}.
We briefly introduce this primitive in Sec.~\ref{sec:YGCbackground} and refer to Yakoubov~\cite{YGCintro} for a more thorough introduction.

The Yao's garbled circuit-based $\FAKE$ construction has two advantages:
\begin{enumerate}
\item 
It is more flexible than other approaches; any notion of distance that can be efficiently computed by a circuit can be used.
In Section~\ref{sec:efficientf}, we describe a suitable circuit for Hamming distance.
The total size of this circuit is $O(\pwlen)$, where $\pwlen$ is the length of the \passwords used.
Edit distance is slightly less efficient, and uses a circuit whose total size is $O(\pwlen^2)$.
\item 
There is no gap between the distances required for functionality and security --- that is, there is no leakage about the \passwords used unless they are similar enough to agree on a key. 
In other words, $\delta = \gamma$.
\end{enumerate}

Informally, the construction involves the garbled evaluation of a circuit that takes in two \passwords as input, and computes whether their distance is less than $\delta$.
Because Yao's garbled circuits are only secure against semi-honest garblers, we cannot simply have one party do the garbling and the other party do the evaluation.
A malicious garbler could provide a garbling of the wrong function --- maybe even a constant function --- which would result in successful key agreement even if the two \passwords are very different.
However, as suggested by Mohassel~\etal~\cite{PKC:MohFra06b} and Huang~\etal~\cite{SP:HuaKatEva12}, since a malicious evaluator (unlike a malicious garbler) cannot compromise the computation, by performing the protocol twice with each party playing each role once, we can protect against malicious behavior.
They call this the \emph{dual execution} protocol.

The dual execution protocol has the downside of allowing the adversary to specify and receive a single additional bit of leakage. 
It is important to note that because of this, dual execution cannot directly be used to instantiate \fPAKE, because a single bit of leakage can be too much when the entropy of the \passwords is low to begin with --- a few adversarial attempts will uncover the entire \password.
Our construction is as efficient as that of Mohassel~\etal and Huang~\etal, while guaranteeing no leakage to a malicious adversary in the case that the \passwords used are not close.
We describe how we achieve this in Section~\ref{sec:YGCbackgroundOurs}. 

%Generalizing this beyond fuzzy PAKE, by adding a secure comparison at the end of our protocol in the style of Mohassel~\etal and Huang~\etal, our technique can be used to evaluate any boolean function in such a way that security holds as long as the correct output is `no'. 
%(That is, if the correct output is `no' then an adversary cannot convince an honest party that it is `yes', and cannot learn any additional bits. 
%If the correct output is `yes', then an adversary can convince an honest party that it is `no', and can also learn an additional bit.) 
%This is sufficient in any scenario where finding a `yes' instance is enough to establish mutual trust.

Due to the symmetric layout of our construction, we skip all $\role$ tags in this section.

\input{tex_files/YGC_background}

\subsection{Construction}
\label{sec:YGCconstruction}

Building a $\FAKE$ from YGC and OT is not straightforward, since all constructions of OT assume authenticated channels, and \FAKE (or \PAKE) is designed with unauthenticated channels in mind.
We therefore follow the framework of Canetti~\etal~\cite{PKC:CDVW12}, who build a UC secure \PAKE protocol using OT.
We first build our protocol assuming authenticated channels, and then apply the generic transformation of Barak~\etal~\cite{C:BCLPR05} to adapt it to the unauthenticated channel setting.
More formally, we proceed in three steps:
\begin{enumerate}
\item 
First, in Section~\ref{sec:rfe}, we define a randomized fuzzy equality-testing functionality $\Frfe$, which is analogous to the randomized equality-testing functionality of Canetti~\etal 
\item
In Section~\ref{sec:rfeprot}, we build a protocol that securely realizes $\Frfe$ in the OT-hybrid model, assuming authenticated channels.
\item
In Section~\ref{sec:ygcfaketransformation}, we apply the transformation of Barak~\etal to our protocol.
This results in a protocol that realizes the ``split'' version of functionality $\Frfe^P$, which we show to be enough to implement to $\FAKE^{P}$.
Split functionalities, which were introduced by Barak~\etal, adapt functionalities which assume authenticated channels to an unauthenticated channels setting. 
The only additional ability an adversary has in a split functionality is the ability to execute the protocol separately with the participating parties.
\end{enumerate}


\input{tex_files/YGC_construction_randomizedfuzzyequality}

\input{tex_files/YGC_construction_randomizedfuzzyequalityprotocol}

\input{tex_files/YGC_construction_transformation}

\input{tex_files/YGC_construction_circuit}
